
\section{Questions}

\paragraph{What is the Fuzzing Type in Your Simulation?} According to the research by Woo, et al. \cite{Woo2013}, the optimal 
Multi-Armed Bandit (MAB) algorithm is highly affected by the fuzzing type (fix-run, fix-time, or ... in a fuzzing) and the
brief metrics. For example, in the Table 2 in their paper \cite{Woo2013}, they showed fix-run, weighted random in rate works best
among the other alternatives in their experiments. However, in your simulation in slides, it seems weighted random in density (FtL) works
best. Therefore, I want to know more information about your simulation, such as fuzzing types, brief metrics you used (other than
$\alpha/\beta$), and so on. This will be the basis of this mathematical problem, so I think it is very necessary to know.

\paragraph{Statistic Significant} I want to know more details of statistic methods you used in your simulation, so that I can 
understand the statistical significant of the simulation results in your slides. This will become the guideline of our mathematical
proof. 

\paragraph{Could You Share Your Simulation Code?} I would be very grateful if you could share your simulation code (using Monte-Carlo?).
From that code, I could understand all the details and I would continue my work basing on your code.

\paragraph{Other Minor Questions} (1) In the simulation, you used crash model instead of bug model. But the reference cited above \cite{Woo2013}
is about bug model. So maybe there is a little difference between your simulation and their works. (2) From the paper \cite{Rebert2014}, 
the scheduling algorithm (this problem) and the seed selection algorithm (cover set) are strong coupled together. However, this will complicate
the problem and we will not consider both of them together at present. (3) There are lots of famous MAB algorithm, such as UCB family, EXP family and 
so on. Have you tried them?

\section{Research Plan}

\paragraph{Simulation} If you could share your code, I will simulate this problem in more details basing on your code. I will try different
fuzzing type, different brief metrics and more MAB algorithms, to see whether "follow the leader" is the most optimal and how it is better than others. 
I have to get a intuitive picture of the computer science aspect of this problem before deeping into the mathematical one.

\paragraph{Mathematical Aspect} I will continue learning some maths. Once I have finished the simulation and got some intuitive picture of the 
problem, I will focus on Markov decision process.


\paragraph{}This is the questions I currently concern about. I will turn to you if I have further questions in the processing of reseaching.

